Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-02-05 R0V0.tex
Redefine set \Xi

\mypara For each index $i\in\mathbb{N}_{[1,N]}$, define the set 
\begin{align}
		\Xi=&\{Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}\ |Y_{pq}:\mathtt{proj}_{\mathscr{K}(i)}(\mathbb{R}^n)\to\mathbb{R},\nonumber\\
		&\mathbin{\mathtt{row}}(Y,p)\in\mathbf{C}(i),\forall p\in\mathbb{N}_{[1,m]},\forall q\in\mathbb{N}_{[1,n]},\nonumber\\
		&i\in\mathbb{N}_{[1,N]}\}\;,
\end{align}
where $Y_{pq}$ is the component of $Y$ located at row $p$ and column $q$, the notation $\mathtt{proj}_{\mathscr{K}(i)}(\mathbb{R}^n)$ stands for the projection of $\mathbb{R}^n$ onto the subset generated by the components of $x$ indexed by $\mathscr{K}$, $\mathbin{\mathtt{row}}(Y,p)$ is the $p$-th row of $Y$ and $\mathbf{C}$ stands for the subset of $\mathbb{R}^n$ generated by the vector having all components zero but those corresponding to the indices defined in $\mathscr{K}$.

>>>>

\mypara Define $\Xi$ as the set of functions $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ with components defined by
\begin{equation*}
		Y_{ij}(\cdot)\begin{cases}
		=Y_{ij}(x_i,\vec{x}_i,u_i)\in\mathbb{R}^{m_i\times n_i},&\text{if}\ (i,j)\in\mathscr{E}_c,\\
		\equiv0_{m_i\times n_i},&\text{otherwise},
		\end{cases}
\end{equation*}
for every $i,j\in\mathscr{V}_c$, and for every $(x_i,\vec{x}_i,u_i)\in\mathbb{R}^{n_i}\times\mathbb{R}^{\vec{n}_i}\times\mathbb{R}^{m_i}$.
